\section{The Proposal}
% \subsection{Exceprts from the Standard (N4296)}
% \subsubesction{CV-Qualifiers (3.9.3)}
% The working draft of the standard (N4296) states the following about cv-qualifiers (3.9.3 CV-qualifiers).
% \begin{enumerate}
%   \item The cv-qualified or cv-unqualified versions of a type are distinct types; however, they shall have the same representation and alignment requirements.
%   \item A compound type (3.9.2) is not cv-qualified by the cv-qualifiers (if any) of the types from which it is compounded. Any cv-qualifiers applied to an array type affect the array element type, not the array type.
%   \item[4] There is a partial ordering on cv-qualifiers, so that a type can be said to be more cv-qualified than another. Table 8 shows the relations that constitute this ordering.
% \end{enumerate}
% \begin{table}[h]
% \centering
% \caption{Relations on const and volatile}
% \begin{tabular}{l l}
% \textit{no cv-qualifier} &$<$ \lstinline {const}\\
% \textit{no cv-qualifier} &$<$ \lstinline {volatile}\\
% \textit{no cv-qualifier} & $<$ \lstinline {const volatile}\\
% \lstinline{const} 		 & $<$ \lstinline {const volatile}\\
% \lstinline{volatile} 	 & $<$ \lstinline {const volatile}\\
% \end{tabular}
% \end{table}
% \subsubsection{Fundamental types (3.9.1)}
% \begin{enumerate}
% \item  Characters can be explicitly declared unsigned or signed. Plain char, signed char, and unsigned char are three distinct types, collectively called narrow
% character types. A char, a signed char, and an unsigned char occupy the same amount of storage and have the same alignment requirements (3.11); that is, they have the same object representation.
% \end{enumerate}
%\subsubsection{Static cast (5.2.9)}
%\subsubsection {Const cast (5.2.11)}
\subsection*{Abstract}
This section will present a short version of the proposal, more example will follow in later sections. There are a view parts which are optional, which means, that those are not necessary to implement the core, though useful.
\subsection{Core Proposal} \label{prop:core}
It shall be possible to declare custom qualifiers, which behave similar to the existing cv-qualifiers. The difference is, that the custom qualifiers have to direct function\footnote{A complier may provide an extension here} as \lstinline {const} would have.\\
A cv-qualifier declares a distinct type, which needs to have the same size and alignmend as the unqualified one\footnote{N4296, 3.9.3}; the same applies to the custom qualifiers.
A so defined qualifier will create additional types, as do the cv-qualifiers. This will enhance the possibilities of type-safety.\\
The relations of the user-defined qualifiers shall correspond to the one of the cv-qualifiers. Also, a qualifier may be added implicitly at any time.
\subsection{Fundamental types}
If a primitve type is used with a custom qualifier, it may be declared, because a qualifier may be added anytime. It does howerver not have any functionality. The newly created type is implicit, so it can be overwritten by an explicit declaration.\\ 
For example, if one declares
\begin{lstlisting}
qualifier q;
q int i = 42;
\end{lstlisting}  
i can be allocated and constructed, since this is the addition of a qualifier, which is always possible. However, no operation can be performed with i, since none is declared. If the qualifier q is void for the type int, one may add an explicit definition, by using a type alias.
\begin{lstlisting}[firstnumber=3]
using q int = int;
\end{lstlisting}
This way q int is the same as int and it fulfills the requirements given for the qualification. So q int can be handled like a normal int.
\subsection{Compound types}
For compound types the rules are the same as given for cv-qualifiers. That is methods can be declared for a qualified this-pointer.
\begin{lstlisting}[firstnumber=4]
struct A
{
	void method() q {};
};
\end{lstlisting}
\subsection{Qualifier cast}
As for cv-qualifiers, the custom qualifier shall only be removeable by \lstinline {const_cast}. It may however be useful to add an alias for this operator, that would be named \lstinline {qualifier_cast}.
\subsection{Scoped qualifier}
The qualifiers shall be declared inside a namespace and importable with the \lstinline {using} syntax. A declaration inside a class shall not be possible. \subsection{Extended type alias (optional)}
The already proposed type alias could be extendend, though that would require more compiler functionality, since it has to assert the right aligment. If for example an atomic type has the same alignment as the type, the following would be possible:
\begin{lstlisting}
qualifier atomic;
template<typename T>
using atomic T = std::atomic<T>;
\end{lstlisting}
This type alias would yield a scope problem though, which will be discussed in a later section (\ref{ana:scope}).
\subsection{Removal qualifier (optional}
Additionally to \lstinline {const} the \lstinline {mutable} keyword is given to override the \lstinline {const} qualification of a member-function. Though that is often considered bad design, this may also be useful for a custom qualifier. To not add a new keyword, I would propose the following syntax:
\begin{lstlisting}
qualifier const;
delete qualifier mutable(const);
\end{lstlisting}
\subsection{Removal blocks (optional)}
Additionally to the removal qualifier, I would propose qualified blocks. That is a qualifier can be removed inside a codeblock with the following syntax:
\begin{lstlisting}
void function(const int i& in)
{
	mutable(in)
	{
		in = 42;
	}
}
\end{lstlisting}
If the qualifier block does not get an argument, the \lstinline {this} pointer is used, if inside a member function, elsewise an error is the result. The main example in mind are thread-safety considerations. 
\begin{lstlisting}
void A::func() threadsafe
{
	locked
	{
		lock_guard<mutex> lock(_mtx);
	}
}
\end{lstlisting}
\subsection{Qualifier deletion (optional)}\label{prop:del}
It may happen that several qualifiers mutually exclude each other (see for example \ref{prop:sign}). Then the combination should be deletable. Deleting a qualifier combination will yield an error, if the deleted combination is declared.
\begin{lstlisting}
qualifier q1;
qualifier q2;
delete q1 q2;
\end{lstlisting}
Since qualifiers can only be declared inside namespaces, this should not have any syntactically side effects.
\subsection{Qualifier alias (optional)}
To make the qualifiers more powerful, two things would be possible: inheritance and compound. If not added explicitly they would however be possible via type alias. The using would allow shorter syntax for several qualifiers and could be done as a workaround via the extended type alias as shown below.  
\begin{lstlisting}
qualifier cv;
template<typename T>
cv T = const volatile T;
\end{lstlisting}
If given the right syntax, this could be stated in a much shorter way:
\begin{lstlisting}
using qualifier cv = const volatile.
\end{lstlisting}
Thereby the qualifier cv becomes an alias here, so the compiler can remove it, what would require more work than the alias version.
\subsection{Qualifier inheritance (optional)}
Another possible feature would be a primitive form of inheritance. Let's consider one defines two qualifiers for thread safety, i.e. read and write safety. The design of the libraries would then imply, that all write-safe actions are also read-safe. So by using the alias one could write:
\begin{lstlisting}
qualifier thread_read, thread_write;
template<typename T>
using thread_write T = thread_read;
\end{lstlisting}
This syntax could be shortened in the following way:
\begin{lstlisting}
qualifier thread_read;
qualifier thread_write : thread_read;
\end{lstlisting} 
Multiple inheritance would of course be possible also.
\subsection{Qualifiers as template parameters (optional)}
If more qualifiers are available, it seems quite obvious, that it could be useful to allow them as template parameters. The syntax would like this:
\begin{lstlisting}
template<qualifier Q>
struct A {Q int i= 42;};
\end{lstlisting}
\subsection{Signed and unsigned (optional)} \label{prop:sign}
Since the \lstinline{signed} and \lstinline{unsigned} keywords fulfill the criteria of the qualifiers\footnote{size and alignment, see N4296 3.9.)} for an integer, they could also be used as qualifiers. The usage of that might seem small, but consider a class which wraps around a numerical value, e.g. a fixpoint class or one for units\footnote{for example boost.units}. There the syntax makes a lot of sense and would allow much easier syntax regarding the conversions.\\
As described in \ref{prop:del} a qualifier deletion would be possible and should be intrinsic for those two keywords.\\
The downside to this would however be the elemination of currently valid code:
\begin{lstlisting}
unsigned u = 42u;//unsigned int
signed s = -1; //signed int
\end{lstlisting}
Another solution, without breaking the code, would be to take int as the standard-type for a sort-of qualifier-declaration. That is:
\begin{lstlisting}
const c = 42; //const int
\end{lstlisting}
I for one, do not consider the declaration of \lstinline {int} via \lstinline {signed} as good style, and would suppose, that it is only used as a convenient template-parameter. That however would be still possible, if qualifiers can be template parameters, so I would promote breaking code.